Error Reporting Parsers: a Monad Transformer Approach

### 2013-08-05 article.tex
parsing: another reference for restricting backtracking
Parsers:  fix egregious typo (change all `<+>`s to `<|>`s)

A form is either a symbol, application, or a special form.  We could just write:
\begin{verbatim}
form = symbol <+> application <+> special
\end{verbatim}

except that the types don't match -- \verb+symbol+'s type parameter is a String, 
whereas the other two have ASTs.  We fix that by mapping the \verb+ASymbol+ 
function over \verb+symbol+:
\begin{verbatim}
form = fmap ASymbol symbol <+> application <+> special
\end{verbatim}

@@

This combinator takes two arguments: an error value and a monadic 
computation.  It first tries to run the computation; if the computation 
fails, it generates an error.  The 
definition of 'failure' is provided by the Alternative instance of \verb+m+.
The reason for its name is that it restricts backtracking and alternatives;
it ``commits" the parser to a do-or-die situation -- either it successfully
parses the input, or the parsing stops.  It's based on the \verb+nofail+
combinator of \cite{hutton1992higher}.

@@

The \verb+form+ parser doesn't have to be changed:
\begin{verbatim}
form = fmap ASymbol symbol <+> application <+> special
\end{verbatim}

>>>>

A form is either a symbol, application, or a special form.  We could just write:
\begin{verbatim}
form = symbol <|> application <|> special
\end{verbatim}

except that the types don't match -- \verb+symbol+'s type parameter is a String, 
whereas the other two have ASTs.  We fix that by mapping the \verb+ASymbol+ 
function over \verb+symbol+:
\begin{verbatim}
form = fmap ASymbol symbol <|> application <|> special
\end{verbatim}

@@

This combinator takes two arguments: an error value and a monadic 
computation.  It first tries to run the computation; if the computation 
fails, it generates an error.  The 
definition of 'failure' is provided by the Alternative instance of \verb+m+.
The reason for its name is that it restricts backtracking and alternatives;
it ``commits" the parser to a do-or-die situation -- either it successfully
parses the input, or the parsing stops.  It's based on the \verb+nofail+
combinator of \cite{hutton1992higher} and also on \cite{Mizushima}.

@@

The \verb+form+ parser doesn't have to be changed:
\begin{verbatim}
form = fmap ASymbol symbol <|> application <|> special
\end{verbatim}
